???A quantitative framework for investigating the reliability of network construction

### 2017-11-16 manuscript/CI_interactions.tex
addressed Kate's comments quickly

    Importantly, empirical descriptions of ecological networks are usually considered to be static representations of the communities and interactions they describe. That is, whether the network is assembled based on aggregated data, a single intensive "snapshot" sample, or expert knowledge, interactions are assumed to occur at the same frequencies wherever and whenever the network is observed~\citep{Olesen2011a}. This assumption conflicts with known variation in interactions over time~\citep{Kitching1987,Olesen2011a} and space~\citep{Kitching1987,Baiser2012} and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}. Taking the variation in interaction frequencies into account would therefore represent a substantial increase in the realism of ecological networks as representations of ecological communities.

@@

    Beyond "true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}). Despite this, the acknowledgment that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.

    In this study, we develop analytical tools to capture the uncertainty in the estimation of pairwise interaction probability. To define the problem, we first discuss the pervasive implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks. We then define a framework which identifies and dissects the different contributions to uncertainty of interaction. We illustrate this framework with a simple quantitative example. Next, we use the framework to provide analytical criteria for improving the sampling of rare interactions. Finally, we offer tangible recommendations for improved descriptors of ecological interactions. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.
    % List of sections may not be accurate any more. Update when paper reaches its final form.

@@

  To define the problem associated with describing ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing an interaction network. This ecologist will be interested in generating a description of the blocks present, and the links between them (Roslin and Majaneva 2017). In other words, he or she seeks to fill in a matrix of species by species interactions. Importantly, the information sought is as much [in] the presence of given links as [in] the absence of others. An observed link will always remain an observed link, but as to why given links are not observed, there may be multiple contributions. Thus, we will set off by contemplating what factors may contribute to links missing from the matrix. We consider that there are three nested levels of uncertainty making the occurrence of any interaction a stochastic process:

@@

    First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics to interact. We define the probability of an interaction $L$ as $P(L)=\lambda$. Obviously, because $k=0$ [[k hasn't been defined up to this point]], it is very likely that they cannot interact even if there were no time or environmental constraints preventing the interaction. [[The previous sentence doesn't follow, k hasn't been defined and we don't know that it's zero. Also, are we assuming that these interactions have been observed over a large area/time like the Kopelke data? Otherwise couldn't something about that particular site prevent species interacting even if they otherwise could?]] But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before. This source of uncertainty is the one documented by trait-matching models~\citep{}. It arises because every model is imperfect and lacks information (i.e. traits) about the constraints on the interaction. In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanishes. [[For species which actually co occur (?)]]

@@

    It could be that the interaction is feasible, i.e. $L=1$, but that it does not occur at a given location or moment in time because there are local constraints [[such as...]] preventing it from occurring. We define the realisation of the interaction process $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions~\citep{}. 
    % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).

@@

    Lastly, measurement errors are always a source of uncertainty in the observation of ecological processes. We define the detection of an interaction $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$. Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions or because of species mis-identification [[or because the interaction is rare enough that we just miss it? Or we're just looking in the wrong place at the wrong time?]]. Some sources of detection error could be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of collected galls), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification).

@@

  It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=0 \cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$. [[k and n still haven't been defined]]% I'm pretty sure this should be L=0 but X=1 and D=1: interaction not feasible but site and detection perfect.

@@

  For the ecologist working on collecting network data, and on later interpreting these data, the considerations above raise a major challenge: how may we infer whether unobserved interactions went undetected due to sampling, or whether they truly do not occur. How then may we refine our sampling approaches to reduce uncertainties, and to gain insights into the impact of multiple processes on field observations? Importantly, some sources [[of uncertainty]] can be minimised with appropriate sampling design and efforts, while other sources are difficult or impossible to reduce – since they are generated by chance variation created by the very process in which we are interested.

  The basic information that we are collecting consists of matrices of interaction partners. Our count of interactions between species A and species B reflects uncertainty with respect to whether two species interact when co-occurring at a given site, chance variation in whether the interaction is realised, [[the previous two things sound like the same thing. Maybe ``whether two species are capable of interacting when co-occuring at a given site, chance variation as to whether the interaction is realized...'']] and uncertainty with respect to whether it is detected when realised. In this case, what can we do to pin down any of these different types of variation?

@@

  The obvious rule of thumb derived from the above example is “sample more”, but we note that there are limits to the utility of this motto. Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction, and it will also increase the probability of detecting unlikely interactions (i.e. interactions occurring with a low probability). Yet, since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions. Thus, the more we sample, the more zeros will appear in our interaction matrix, which may seem like a counter-intuitive outcome. [[Furthermore, depending on the spatial and temporal extent of our sampling, more sampling may not help us detect feasible interactions which are prevented from being realized by local processes at the sites/times we are sampling.]]

@@

  [[How do we define samples? For the Kopelke set we use sampling occasion, but what about sampling twice as many trees on the same day and same place? Does that count? Does it have to be spatially and/or temporally separated? Is it relevant??]]

@@

          In the literature of ecological networks there is a solid collection of data for which we know network connectance and from which we can define the connectance distribution. Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species. It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other. If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,[[from the literature or from our network?]] then the beta parameters could be computed as follows using the method of moments:

@@

  %Perhaps we want to also have a trait matching example in addition to the degree distribution example below?
  % Are degree distributions valid priors for interaction probabilities in a unipartite web? For the Salix-gall dataset we're using interaction probabilities as priors (since the degree of both Salix and galler matter)... maybe we should rephrase this to predict the degree of species $i$ based on the degrees of 10 other species in the network?
  The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $X = 3$[ = k?] observations of interactions. The maximum likelihood estimate of the interaction probability is simply $\theta_{MLE} = 3/10 = 0.3$. 
  % We should probabaly have a value  on the interaction probablitity that differs from the average of the degree distrbution
   Now consider we know that species $i$ is known to interact with 10 other species, which have the following normalised degrees:

@@

    Adding the observed data (n=10, k=3) and using the same code,
    we obtain posterior hyper parameters $\alpha'$=4.05083 and $\beta'$=12.36589 and a posterior mean 0.247 and variance 0.011 for the probability of [[...?]]. Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data has reduced the variance.

@@

    The exercise exemplified above yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}). Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$ [[shouldn't it just be ``no observation of the two species co-occuring, $n=0$.'' I.e. nothing about failing to interact? Wouldn't that be $n = k$ and then you're pretty certain that an interaction does indeed exist?]] In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur; see above).

@@

    It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}. Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$; the remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one. It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics. Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric. For instance, assume that among all pairs of species with few observed co-occurrences there are many pairs which truly interact.    If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution. While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$ no analytical solution currently exists for uncertain $\lambda$. Instead we must rely on computer simulations. In the following section, we will provide an empirical example, based on the data set published by~\citet{Kopelke2017}. We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics. We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed [[to be]] fixed entities.

@@

      With species $i$ and $j$ co-occurring at all 374 sites and never being observed to interact, the maximum likelihood expectation for the probability of an interaction $ij$ is very close to 0 and the variance about this estimate is very narrow. In other words, we could establish with high certainty that the species will never interact. However, for most [[all??]] pairs of species $i$ and $j$, the species did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior. Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).

@@

      As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean. This is again straightforward to do in R (see the function ``credible interval" in \emph{Appendix S2}). Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction [[ were there any species with 50 co-occurrences and no interaction?]] (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases. In no case, however, does the confidence interval include 0. Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero (Table~\ref{interval_table}). In other words, even with a very large data set, we will have problems in establishing that a given species pair can never interact.

@@

      Rather than calculating confidence intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.5, 0.1, or 0.01, we would need six, 51, and 101 observed co-occurrences with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}). 
      Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-parasitoid network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25 and 101 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1 and 0.01, respectively.
      Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species. Even in the extensively replicated \emph{Salix}-galler-parasitoid dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-parasitoid pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1 [[were there any pairs that interacted 51 times (or 25 for galler-parasitoid) and didn't interact at all?]], and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01). Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.

@@

    \begin{figure}[ht]
    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-parasitoid networks), and links per consumer (gallers in the \emph{Salix}-galler networks and parasitoids in the galler-parasitoid networks) for networks assembled using posterior distributions based on~\citet{Barbour2016,Barbour2016Dryad}. We created 100 "posterior-sampling" networks and then, for each of these, created 100 "detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network. This simulates imperfect detection of interactions in the field. Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks. For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties and the value of each property decreases with the proportion of links included in the detection-filter networks.}
    \label{posterior_webs}    
    \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
    \end{figure}

@@

  [Here we need to be very hands-on and remember the invitation letter form Ecol Letters:
  As a contribution primarily to methodology, the manuscript will not be considered for "Ideas \& Perspectives". (Please recall my message concerning your past presubmission inquiry.) However, Ecology Letters is entertaining the idea of a new section for "Novel Methods". As we have not advertised this, I would ask you to keep that information in confidence. If acceptable to an Associate Editor and reviewers, your paper could be the first, or one of the first, contributions to this new section. Accordingly, the work would be subject to considerable scrutiny and I would urge you to make the paper as strong as you can. This would include demonstrating the need for this new method (i.e. outlining how this is different than other approaches currently in use and how they fail at some important task), documenting the robustness and accuracy of the approach, performing case study, and making robust high-quality code freely available.]

>>>>

    Importantly, empirical descriptions of ecological networks are usually considered to be static representations of the communities and interactions they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur at the same frequencies wherever and whenever the network is observed~\citep{Olesen2011a}. This assumption conflicts with known variation in interactions over time~\citep{Kitching1987,Olesen2011a} and space~\citep{Kitching1987,Baiser2012} and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}. Taking the variation in interaction frequencies into account would therefore represent a substantial increase in the realism of ecological networks as representations of ecological communities.

@@

    Beyond ``true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}). Despite this, the acknowledgment that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.

    In this study, we develop analytical tools to capture the uncertainty in the estimation of pairwise interaction probability. To define the problem, we first discuss the pervasive implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks. We then define a framework which identifies and dissects the different contributions to uncertainty of interaction. We illustrate this framework with a simple quantitative example. Next, we use the framework to provide analytical criteria for improving the sampling of rare interactions. Finally, we offer tangible recommendations for improved descriptors of ecological interactions. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.

@@

  To define the problem associated with describing ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing an interaction network. This ecologist will be interested in generating a description of the blocks present, and the links between them (Roslin and Majaneva 2017). In other words, he or she seeks to fill in a matrix of species by species interactions. Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. An observed link will always remain an observed link, but as to why given links are not observed, there may be multiple contributions. Thus, we will set off by contemplating what factors may contribute to links missing from the matrix. We consider that there are three nested levels of uncertainty making the occurrence of any interaction a stochastic process:

@@

    First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics to interact. We define the probability of an interaction $L$ as $P(L)=\lambda$. Obviously, because $k$ (the number of observed interactions) is 0, it is possible that the two species cannot interact even if there were no time or environmental constraints preventing the interaction. 
    % [[The previous sentence doesn't follow, k hasn't been defined and we don't know that it's zero. Also, are we assuming that these interactions have been observed over a large area/time like the Kopelke data? Otherwise couldn't something about that particular site prevent species interacting even if they otherwise could?]] 
    % [[With defining k I think this is fine... site uncertainty will come in later, and it's not necessary to assume anything about the sampling design to get from not observing two species to interact to suspecting that they don't (degree of confidence depending on the species involved). I've toned down "very likely" to "possible" though - does that help?]]
    But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before. This source of uncertainty is the one documented by trait-matching models~\citep{}. It arises because every model is imperfect and lacks information (i.e. traits) about the constraints on the interaction. In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanishes. 
    % [[For species which actually co occur (?)]]
    % [[I think that gets covered under "sufficient sampling"]]

@@

    It could be that the interaction is feasible, i.e. $L=1$, but that it does not occur at a given location or moment in time because there are local constraints, such as inclement weather or lack of suitable habitat, that prevent the interaction from occurring. We define the realisation of the interaction process $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions~\citep{}. 
    % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).

@@

    Lastly, measurement errors are always a source of uncertainty in the observation of ecological processes. We define the detection of an interaction $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$. Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions, because of species mis-identification, or because the interaction is very rare. Some sources of detection error could be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification).

@@

  It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=0 \cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurances. % I'm pretty sure this should be L=0 but X=1 and D=1: interaction not feasible but site and detection perfect.

@@

  For the ecologist working on collecting network data, and on later interpreting these data, the considerations above raise a major challenge: how may we infer whether unobserved interactions went undetected due to sampling, or whether they truly do not occur. How then may we refine our sampling approaches to reduce uncertainties, and to gain insights into the impact of multiple processes on field observations? Importantly, some sources of uncertainty can be minimised with appropriate sampling design and efforts, while other sources are difficult or impossible to reduce – since they are generated by chance variation created by the very process in which we are interested.

  The basic information that we are collecting consists of matrices of interaction partners. Our count of interactions between species A and species B reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site, chance variation in whether the interaction is realised,  and uncertainty with respect to whether it is detected when realised. In this case, what can we do to pin down any of these different types of variation?

@@

  The obvious rule of thumb derived from the above example is ``sample more", but we note that there are limits to the utility of this motto. Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction, and it will also increase the probability of detecting unlikely interactions (i.e. interactions occurring with a low probability). Yet, since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions. Thus, the more we sample, the more zeros will appear in our interaction matrix, which may seem like a counter-intuitive outcome.

@@

  % [[How do we define samples? For the Kopelke set we use sampling occasion, but what about sampling twice as many trees on the same day and same place? Does that count? Does it have to be spatially and/or temporally separated? Is it relevant??]]
  % [[Pretty sure this will always depend on the study - also seems like a pretty large digression.]]

@@

          In the literature of ecological networks there is a solid collection of data for which we know network connectance and from which we can define the connectance distribution. Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species. It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other. If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,
          % [[from the literature or from our network? Has to be from the literature - if it was our network we'd know way more than just C]] 
          then the beta parameters could be computed as follows using the method of moments:

@@

  %Perhaps we want to also have a trait matching example in addition to the degree distribution example below?
  % Are degree distributions valid priors for interaction probabilities in a unipartite web? For the Salix-gall dataset we're using interaction probabilities as priors (since the degree of both Salix and galler matter)... maybe we should rephrase this to predict the degree of species $i$ based on the degrees of 10 other species in the network?
  The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions. The maximum likelihood estimate of the interaction probability is simply $\theta_{MLE} = 3/10 = 0.3$. 
  % We should probabaly have a value  on the interaction probablitity that differs from the average of the degree distrbution
   Now consider we know that species $i$ is known to interact with 10 other species, which have the following normalised degrees:

@@

    Adding the observed data (n=10, k=3) and using the same code,
    we obtain posterior hyper parameters $\alpha'$=4.05083 and $\beta'$=12.36589 and a posterior mean 0.247 and variance 0.011 for the probability of interaction. Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data has reduced the variance.

@@

    The exercise exemplified above yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}). Note the special case where there is no observation of the two species co-occurring, $n = 0$  In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur; see above).

@@

    It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}. Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$; the remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one. It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics. Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric. For instance, assume that among all pairs of species with few observed co-occurrences there are many pairs which truly interact.    If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution. While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$ no analytical solution currently exists for uncertain $\lambda$. Instead we must rely on computer simulations. In the following section, we will provide an empirical example, based on the data set published by~\citet{Kopelke2017}. We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics. We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed to be fixed entities.

@@

      With species $i$ and $j$ co-occurring at all 374 sites and never being observed to interact, the maximum likelihood expectation for the probability of an interaction $ij$ is very close to 0 and the variance about this estimate is very narrow. In other words, we could establish with high certainty that the species will never interact. However, for most pairs of species $i$ and $j$, the species did not co-occur at many sites and our posterior mean and variance retain some of the influence of the prior. Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).

@@

      As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean. This is again straightforward to do in R (see the function ``credible interval" in \emph{Appendix S2}). Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases. In no case, however, does the confidence interval include 0. Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero (Table~\ref{interval_table}). In other words, even with a very large data set, we will have problems in establishing that a given species pair can never interact.

@@

      Rather than calculating confidence intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.5, 0.1, or 0.01, we would need six, 51, and 101 observed co-occurrences with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}). 
      Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-parasitoid network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25 and 101 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1 and 0.01, respectively.
      Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species. Even in the extensively replicated \emph{Salix}-galler-parasitoid dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-parasitoid pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1, and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01 [[Do we need the other thresholds? Seems like it'll get redundant]]). Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.

@@

    \begin{figure}[ht]
    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-parasitoid networks), and links per consumer (gallers in the \emph{Salix}-galler networks and parasitoids in the galler-parasitoid networks) for networks assembled using posterior distributions based on~\citet{Barbour2016,Barbour2016Dryad}. We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network. This simulates imperfect detection of interactions in the field. Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks. For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties and the value of each property decreases with the proportion of links included in the detection-filter networks.}
    \label{posterior_webs}    
    \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
    \end{figure}

@@

  [Here we need to be very hands-on and remember the invitation letter form Ecol Letters:
  As a contribution primarily to methodology, the manuscript will not be considered for ``Ideas \& Perspectives". (Please recall my message concerning your past presubmission inquiry.) However, Ecology Letters is entertaining the idea of a new section for ``Novel Methods". As we have not advertised this, I would ask you to keep that information in confidence. If acceptable to an Associate Editor and reviewers, your paper could be the first, or one of the first, contributions to this new section. Accordingly, the work would be subject to considerable scrutiny and I would urge you to make the paper as strong as you can. This would include demonstrating the need for this new method (i.e. outlining how this is different than other approaches currently in use and how they fail at some important task), documenting the robustness and accuracy of the approach, performing case study, and making robust high-quality code freely available.]
